The problem and promise of scale in animal social multilayer networks

### 2020-02-10 paper/manuscript.Rmd
conclusion edits

Silk et al. (2018) presented some key multilayer questions in animal behaviour
research. While these questions represent an important starting point for
multilayer networks, we present an additional set of questions relevant to the
promise and problem of scale in mutlilayer networks:

1. How do social phenotypes across scales differently influence fitness? Are
some temporal or social scales better predictors for different fitness metrics?

@@

3. How, and why, does the spatial scale of perception influence, e.g. auditory,
visual, or chemotaxis, influence the  social environment across scales? What is
the role of memory, and by extension social and spatial cognition, as animals
navigate their environment and make decisions about where to move next?

>>>>

Silk et al. (2018) summarized some key multilayer questions in animal behaviour
research. While these questions are important for linking animal behaviour and
multilayer networks, we present an additional set of questions posed through the
lense of spatial ecology and relevant to the promise and problem of scale in
mutlilayer networks:

1. How do social phenotypes vary across social scales and differentially influence fitness? Are
some temporal or social scales better predictors for different fitness metrics?

@@

3. How, and why, does the spatial scale of perception influence, e.g. auditory,
visual, or chemotaxis, influence the  social environment? What is
the role of memory, and by extension social and spatial cognition, as animals
navigate their environment and make decisions about where to move next?
